---
Title: ⛰️ Discover Brown Mountain!
---

Brown Mountain offers 34 miles of trails for ATV, Trail bikes and Four-wheel drive! The trails cover all the levels of difficulty from easy to very challenging! 

## Trails Overview: 

```{r}
#| echo: false
suppressMessages(library("sf"))
library(leaflet)
library(htmltools)  
b_mt <- sf::st_read("data/brown_mountain.gpkg", layer = 'trail', quiet = TRUE)
POI <- data.frame(
  type = c("Parking", "Campsite", "Fee Station"),
  lat = c(35.8973062,
          35.8934043,
          35.8894143),
  lng =c(-81.7604145,
         -81.7438603,
         -81.7394553
  )
)

b_mt <- sf::st_transform(b_mt, 4326)

```



```{r}
#| echo: false

base <- leaflet() |>
  addTiles()  |>
  addMarkers(lng = POI$lng, lat = POI$lat, popup = POI$type)

base |> 
  addPolylines(data = b_mt)

```


## Check the difficulty and if your vehicle is authorized

Trail bikers are free to use all the trails but there are more restrictions on drivers of ATV and Four-wheel drive vehicles (4WD).

Green represents the easiest trails, yellow tends to provide more challenges and black are the hardest ones. 

Enjoy!


```{r}
#| echo: false

factpal <- colorFactor(c("green", "yellow", "black"), b_mt$difficulty)
 
base |> 
  addPolylines(data = b_mt, color = ~factpal(b_mt$difficulty), popup = ~htmlEscape(vehicule)) 


``` 

## Additional resources: 

- [Doe Mountain](https://dmra.gov/), Tennessee for additional nearby offroad adventures

- Site of the first school of forestry in the US:  [https://www.fs.usda.gov/r08/northcarolina/recreation/cradle-forestry](https://www.fs.usda.gov/r08/northcarolina/recreation/cradle-forestry)


- A local brewery: [https://fontaflora.com/location/whippoorwill-farm/](https://fontaflora.com/location/whippoorwill-farm/)

## Leave No Trace!

Remember to pack out what you pack in!  

